Structured Versus Decorated Cospans

### 2020-11-16 cospans.tex

\begin{thm} \label{thm:equiv}
Suppose $\ca{A}$ has finite colimits and $(F,\phi,\phi_0)\maps(\ca{A},+) \to (\bicat{Cat},\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor.   Then the symmetric monoidal double category $F\lCsp$ of decorated cospans is equivalent to the symmetric monoidal double category $_L\lCsp(\inta F)$ of structured cospans, where $L \maps \A \to \inta F$ is the left adjoint of the induced Grothendieck opfibration $U \maps \inta F \to \A$.
\end{thm}

The conditions of the above theorem relate to the existence of left adjoints for opfibrations; we first sketch this underlying framework, and then we proceed to the proof of the theorem. The basics of fibration theory needed for our purposes are recalled in \cref{sec:fibrations}.

>>>>

\begin{thm} \label{thm:equiv}
Suppose $\ca{A}$ has finite colimits and $F \maps(\ca{A},+) \to (\bicat{Cat},\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor.   Then the symmetric monoidal double category $F\lCsp$ of decorated cospans is equivalent to the symmetric monoidal double category $_L\lCsp(\inta F)$ of structured cospans, where $L \maps \A \to \inta F$ is the left adjoint of the induced Grothendieck opfibration $U \maps \inta F \to \A$.
\end{thm}

The conditions of the above theorem relate to the existence of colimits as well as left adjoints for opfibrations. We first sketch this underlying framework, and then we proceed to the proof of the theorem. The basics of fibration theory needed for our purposes are recalled in \cref{sec:fibrations}.
